---
title: "Problem Set #4"
author: "Shivani Aggarwal"
date: "February 24, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Load needed dependencies

library(tidyverse)
library(devtools)
library(gt)
library(forcats)

```


```{r data, echo=FALSE}


```

## Question 1

```{r question, echo=FALSE}


```

There were `r ` respondents who supported the Democratic candidate.

There were `r ` more respondents who favored the Republican candidate than who were Undecided.

There are two gender variables (gender and gender_combined). There are `r ` individuals for whom these variables have different values.

There are `r ` respondents listed as “White” under race_eth who are not listed as “White” under file_race_black.

The first response of Dem came `r ` minutes (rounded to the nearest minute) before the first response of Rep.

## Question 2

```{r table, echo=FALSE, results="asis"}



```

## Question 3

```{r violin, echo=FALSE}


  

```

## Question 4

```{r visual, echo=FALSE}


```


